\chapter{Original Introduction}
\chapterprecis{Simon Gleave}
\newline
\newline
I first hatched the idea of putting together a comprehensive document to cover 
all aspects of the World Cup when I saw Eric Visser's guide to the Asian World
Cup qualifying tournament last October. It struck me that as England were 
effectively out, I could view this year's tournament on an unbiased level and
therefore write a preview of the World Cup which would be balanced. In addition
to a simple preview, I thought it would be a good idea to persuade the 
international community of RSS to write articles about their own national sides.
This would be a fairly unique way of looking at the World Cup finals.

I was fairly pessimistic about getting these country profiles in time, but I was
also worried that certain countries would be impossible to get hold of. The 
latter fear proved well founded as I was unable to find anybody to write on 
Bulgaria, Cameroon, Morocco, Saudi Arabia and Russia, but 19 out of 24 isn't 
bad and some of the profiles are quite superb, giving an insight that we 
wouldn't otherwise have.

I have left the profiles in the style in which they were written, and have only
corrected for English and brevity (in some cases). There is information on the
five nations that were not collected, kindly sent to me by Tim Aitchison. I'd 
also like to thank the multiplicity of contributors without whom this could
never have been written.

So, enough of me, you want to know what's contained in this document that has 
taken nearly 9 months to put together, don't you?

Oh, I should just finally say that if you think improvements can be made, please 
e-mail me and I'll try to update things before the finals start on June 17.
