\chapter{Preview of Group A}
\chapterprecis{Simon Gleave}
\newline
\newline
\begin{figure}[H]
\small
\begin{tabular}{l c c c c c c c l}
Group A & Played & Won & Drawn & Lost & For & Agst & Apps & Best Performance\\ \hline
Colombia & 7 & 1 & 2 & 4 & 9 & 15 & 2 & Second Round (1990) \\
Romania & 12 & 3 & 3 & 6 & 16 & 20 & 2 & Second Round (1990)\\
Switzerland & 18 & 5 & 2 & 11 & 28 & 44 & 6 & Quarter Final (1954)\\
United States & 10 & 3 & 0 & 7 & 14 & 29 & 3 & Semi-Final (1930) \\ \hline
\end{tabular}
\normalsize
\end{figure}
The most open of the six groups in the final, and it will probably turn out to
produce the most exciting games. The reason for this is that Colombia, Romania 
and Switzerland all put more emphasis on attack than defence and the USA will
feel that they must put a show on for their fans in their own country. We can
therefore expect plenty of goals from these four teams, but how will the group
shape up? Well, as you can see from the records above, none of these four have
been World beaters in the past and so none have much of a World Cup pedigree. 
However, Colombia are overwhelming favourites to take the group and are as low
as 8-1 to win the trophy itself. This is plainly nonsense and is a complete
overreaction to their 5-0 win in Argentina during qualifying - they undoubtedly
have highly talented players in Valderrama and Asprilla but they have not
suddenly leapt from big outsiders in 1990 to one of the favourites in 1994. For
this reason, I am inclined to look elsewhere for the group winners although
Colombia should progress from Group A.

Switzerland are my choice to win Group A, they have a superb tactician as a 
coach and players like Chapuisat and Knup are undoubtedly World class. Their 
achilles heel is in defence, which could be a problem with the attacking sides
in Group A, but the Swiss should just scrape top place.

Romania are an interesting side due to their constant underachievement in World
Cup finals - in 1990, they had some outstanding talent in Hagi, Popescu and 
Lacatus, but having reached the second round, they found Ireland's defence too
strong and tamely lost in a penalty shoot-out. This time they should again 
progress because of their attacking prowess, but the first team to play a 
defensive game against Romania will probably put them out.

This leaves the hosts, and unfortunately, there doesn't seem to be a place for
them - no host nation has ever failed to get past the first round phase, but I
think the USA are about to rewrite this statistic. In a group of outstanding
attacking sides, the USA will really be up against it and will need goalkeeper,
Tony Meola to be on outstanding form to prevent 3 defeats.

So, Switzerland to win Group A, Colombia to finish runners-up with Romania 
progressing as one of the best third place teams.
