\chapter{Preview of Group C}
\chapterprecis{Simon Gleave}
\newline
\newline
\begin{figure}[H]
\small
\begin{tabular}{l c c c c c c c l}
Group C & Played & Won & Drawn & Lost & For & Agst & Apps & Best Performance\\ \hline
Bolivia & 3 & 0 & 0 & 3 & 0 & 16 & 2 & First Round (1930, 1950) \\
Germany & 62 & 36 & 13 & 13 & 131 & 77 & 10 & Winners ('54,'74,'90) \\
South Korea & 8 & 0 & 1 & 7 & 5 & 29 & 3 & First Round ('54,'86,'90) \\
Spain & 32 & 13 & 7 & 12 & 43 & 38 & 8 & Fourth (1950) \\ \hline
\end{tabular}
\normalsize
\end{figure}
On paper, this looks like a straight fight between Germany and Spain, but the
presence of Bolivia, conquerors of mighty Brazil in qualifying and South Korea,
who have always threatened to cause a shock complicate matters to a degree.

Bolivia qualified for the finals for the first time since 1950 mainly due to 
their phenomenal home record in the altitude of La Paz. It's extremely
difficult to make a fair judgement on their chances because of this, but there
may have been a clue when they played Ireland in Dublin recently and gave the
Irish a real fright before conceding a late goal to go down 1-0 - don't write
these South Americans off.

Germany have got an astonishing record in World Cup finals, they've reached the
final in four of the last six tournaments, winning twice and are of course, the
current holders. However, their form has been rather suspect of late and it is
possible that the ageing squad will not perform as well as usual this time 
around. Having said that, the Germans can never be written off in major
tournaments and they should progress from this group with relative ease.

South Korea have appeared in the last 2 World Cup finals and have looked like
they might pull off a shock without ever doing so. All of their players have 
plenty of skill and the goals that they've scored in final tournaments have
always been spectacular. However, this group looks to be tougher than either
of the groups they graced in '86 and '90 and I'm afraid they'll find it very
hard to rise above the basement.

Finally, in this group, we have Spain, the perennial enigma of World Cup finals.
The Spanish have always underachieved in this tournament, they are reckoned to
be one of Europe's strongest teams and yet their World Cup performances hardly 
underline this - in 1982, as hosts, they managed to lose to minnows Northern
Ireland before tamely going out in the second round. However, this time they
have a new young team and are said to have more spirit than is usually 
associated with Spanish teams. They came through an extremely tough group,
surviving the loss of their goalkeeper, Zubizaretta early in the final game,
and with this added steel, I wouldn't be surprised to see them take this group,
and then go on to their best World Cup finish since 1950.

Spain and Germany will qualify from Group C with Bolivia waiting to see if
their third place is enough and South Korea propping the table up again.
