\chapter{Switzerland}
\chapterprecis{Serge Pasche}
\newline
\newline
Coach: Roy Hodgson
\begin{figure}[H]
\begin{tabular}{c c l l c c c}
P & & & Club & Age & Caps & Goals \\ \hline
G & 1 & Marco Pascolo & Servette Geneve & 28 & 16 & 0 \\
G & 12 & Stefan Lehmann & FC Sion & 31 & 4 & 0 \\
G & 22 & Martin Brunner & Grasshoppers Zurich & 31 & 33 & 0 \\ \hline
D & 2 & Marc Hottiger & FC Sion & 27 & 36 & 3 \\
D & 3 & Yvan Quentin & FC Sion & 24 & 10 & 0 \\
D & 4 & Dominique Herr & FC Sion & 29 & 35 & 2 \\
D & 5 & Alain Geiger & FC Sion & 34 & 91 & 2 \\
D & 13 & Andy Egli & Servette Geneve & 36 & 75 & 8 \\
D & 18 & Martin Rueda & FC Luzern & 31 & 4 & 0 \\
D & 19 & Juerg Studer & FC Zurich & 28 & 5 & 0 \\ \hline
M & 6 & Georges Bregy & Young Boys Bern & 36 & 47 & 14 \\
M & 7 & Alain Sutter & FC N{\”u}rnberg (Ger) & 26 & 43 & 3 \\
M & 8 & Christophe Ohrel & Servette Geneve & 25 & 25 & 4 \\
M & 10 & Ciriaco Sforza & FC Kaiserslautern (Ger) & 24 & 20 & 3 \\
M & 16 & Thomas Bickel & Grasshoppers Zurich & 30 & 39 & 3 \\
M & 17 & Sebastien Fournier & FC Sion & 23 & 3 & 1 \\
M & 20 & Patrick Sylvestre & Lausanne Sports & 26 & 8 & 0 \\
M & 21 & Thomas Wyss & FC Aarau & 28 & 5 & 0 \\ \hline
F & 9 & Adrian Knup & VfB Stuttgart (Ger) & 26 & 31 & 21 \\
F &11 & Stephane Chapuisat & Borussia Dortmund (Ger) & 25 & 33 & 9 \\
F &14 & Nestor Subiat & FC Lugano & 28 & 3 & 3 \\
F &15 & Marco Grassi & FC Zurich & 26 & 8 & 2 \\ \hline
\end{tabular}
\end{figure}
\section{Information}
Switzerland is a small country (42000 square km) between France, Germany, 
Austria and Italy. It has 6.5 million inhabitants and the main cities are 
Geneva, Bern (capital), Zurich and Basel.
Switzerland has 4 different cultures, and the official languages are German, 
French, Italian and Romantsch.

\section{WC 94 Qualification}
Switzerland qualified in the European Group 1. They took 3 points to Italy and ended in second position.
\begin{figure}[H]
\begin{tabular}{l c c c c c c c}
European Group 1 & GP & W & D & L & GF & GA & Pts \\ \hline
\textbf{Italy} & 10 & 7 & 2 & 1 & 24 & 8 & 16 \\
\textbf{Switzerland} & 10 & 6 & 3 & 1 & 23 & 6 & 15 \\
Portugal & 10 & 6 & 2 & 2 & 19 & 7 & 14 \\
Scotland & 10 & 4 & 3 & 3 & 14 & 13 & 11 \\
Malta & 10 & 1 & 1 & 8 & 3 & 23 & 3 \\
Estonia & 10 & 0 & 1 & 9 & 1 & 27 & 1 \\ \hline
\end{tabular}
\end{figure}
\section{Friendlies}

01.94   USA - Switzerland 1-1
01.94   Mexico - Switzerland 1-5
03.94   Hungary - Switzerland   1-2
04.94   Switzerland - Czech Rep 3-0
05.94   Switzerland - Liechtenstein 2-0
05.94   Italy - Switzerland   1-0
06.94   Bolivia - Switzerland   0-0

Switzerland are one of the emerging forces in European football, but not many 
people are taking this into account when assessing the 1994 World Cup finals.
Switzerland will be a surprise team as, yet again, they are being 
underestimated, and Italy can testify that underestimating this Swiss team can
be very costly.

The coach, Englishman Roy Hodgson has been in charge for three years now, and
the team is extremely well organised. Switzerland are a fluid attacking force
and their matches are usually full of incident.

Switzerland should easily get through the first round phase in either 1st or 
2nd place in Group A. They are capable of beating any team other than Germany
or Brazil, and I therefore see them reaching the quarter finals.

\section{Key Players}
STEPHANE CHAPUISAT (Forward, Borussia Dortmund(GER)):
The finest Swiss player at keeping possession, he can score at any moment. 
Chapuisat has played in the German Bundesliga since 1991 and has excellent
experience at international level. He was named "Player of the year" in Germany
in 1992.

ADRIAN KNUP (Forward, VfB Stuttgart(GER)):
21 goals in 31 games. He is faster than Chapuisat but has less technique. 
Scores a lot of headers.

CIRIACO SFORZA (Midfield, Kaiserslautern(GER)):
One of the best attacking midfielders in the German Bundesliga. Very active 
player with good skill.

ALAIN SUTTER (Midfield, FC N{\”u}rnberg(GER)):
Good crosser from the left side, excellent technique.

MARC HOTTIGER (Defender, FC Sion):
Fastest defensive player, very attacking right back.
